---
title: "R Markdown"
subtitle: "Slides available at UPDATE THIS LINK!! [GitHub](https://github.com/Chris-M-P/Questionnaire-scoring-protocols)"
author: "Chris Penfold"
date: "26 October 2018"
output:
 ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Overview

## Goals

1. To understand what R Markdown is (and isn't)
2. To be able to make your own output from R Markdown
3. To be able to apply R Markdown to your own work
    + Or know that it's not for you!

## Outline

### **Lecture** + Tutorial

1. What is R markdown?
2. What can you use R Markdown for?
3. How does it work?

## Outline

### Lecture + **Tutorial**

Make your own R markdown document

## What is R Markdown?

## Possible uses

1. Quick report
    + R Notebooks
2. Full research paper
3. Presentation
4. PhD thesis...
5. Web page
6. eBook
7. Blog etc...

## Example 

*"Could you just re-run this with..."*



## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slide with inline maths

- You can insert results of R code using 3 backticks \`\`\`

    <code>
    \`\`\`{r}  
    code here  
    \`\`\`  
    </code>

- You can also do this 'inline' like this <code> \` r 2 + 3 \` </code> , but only the results are shown

    `r 2 + 3`

- Simple maths example

```{r, echo=TRUE}
2 + 3
```

- To do this I typed

\`\`\`{r}  
2 + 3  
\`\`\`



## R Notebook - standalone R Markdown documents

+ R Notebooks are a specific use of R Markdown
+ Code and output are combined in a single document
+ R Notebooks can not execute code outside the Notebook (e.g. messy data processing etc.)
+ Particularly suited to quick reports where having embedded code is not a problem
+ Restricted to html output
+ Good for archiving analyses and sharing results with collaborators

## R Notebook 

An R Notebook is a special execution mode of R Markdown with two characteristics that make it very useful for communicating results (from <https://www.r-bloggers.com/communicating-results-with-r-markdown/>:

+ Rendering a preview of an R Notebook does not execute R code, making it computationally convenient to create reports during or after interactive analyses.
+ R Notebooks have an embedded copy of the source code, making it convenient for others to examine your work.

## R Notebook - example

## Times to use R Markdown

|PROBLEM |	COMMON TOOL |	BETTER TOOL|
|--------|--------------|-------------|
|Share reports and presentations	| Microsoft Office |	R Markdown|
|Summarize and share your interactive analyses	| R Scripts	| R Notebooks|


## R Markdown - Key limitations

+ Tables
+ How does this fit into a typical paper writing workflow?

## Useful links

* RStudio R Markdown resources - <https://rmarkdown.rstudio.com/>
* *R Markdown: The Definitive Guide* - [link](https://bookdown.org/yihui/rmarkdown/)
* R Markdown cheatsheet - [link](http://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf)
    + Also available from RStudio:
    + *Help > Cheatsheets > R Markdown Cheat Sheet*
* Stackoverflow `Rmarkdown` tag - <https://stackoverflow.com/questions/tagged/r-markdown>
    